---
title: "Call Center Data Analysis"
author: "jinyoung, hyunah, suyoung, yunhwan"
date: '20170807'
output:
  html_document: default
  word_document: default
---

# Call data import
```{r error=FALSE,message=FALSE,warning=FALSE}
# Read data
#setwd("C:/CallCenter")
data<-read.csv("domino7.csv", header=TRUE)
data2<-read.csv("mister3.csv", header=TRUE)

# Remove NA
data<-data[complete.cases(data),]
data2<-data2[complete.cases(data2),]


data$holiday <- as.factor(data$holiday)
data2$holiday <- as.factor(data2$holiday)

```

# Install Library
```{r error=FALSE,message=FALSE,warning=FALSE}
library(rpart.plot)
library(gplots)
library(xts)
library(dplyr)
library(tidyr)
library(ggplot2)
library(sqldf)
require('gridExtra')
```  
# (1) DAILY(7DAYS)
## x:daily(7days), y:count
```{r error=FALSE,message=FALSE,warning=FALSE}
# Domino
count = as.numeric(as.factor(data$count))
c_data <- as.xts(count, order.by=as.Date(data$date))
c_weekly <- apply.weekly(c_data, mean)

# Mister
count2 = as.numeric(as.factor(data2$count))
c_data2 <- as.xts(count2, order.by=as.Date(data2$date))
c2_weekly <- apply.weekly(c_data2,mean)

# Make a graph
par(mfrow = c(1, 2))
plot(c_weekly, main="Domino", xlab="daily(7days)", ylab="count", xlim=c(0,1000))
plot(c2_weekly, main="Mister",xlab="daily(7days)", ylab="count", xlim=c(0,1000))
```

# (2) TIME
## DATA PREPROCESSING
```{r error=FALSE,message=FALSE,warning=FALSE}
# Domino
ty_data = data %>%
  group_by(time,year) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

# Mister
ty_data2 = data2 %>%
  group_by(time,year) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))
```

## x:time, y:count, gb:year
* highest number of calls for dinnertime
* lowest for opening/closing time
```{r error=FALSE,message=FALSE,warning=FALSE}
## Make a graph
# Domino
p1 <- ggplot(ty_data,aes(x=time,y=count,group=year,color=year)) + 
  geom_line(aes(color=year)) + 
  geom_point() +
  scale_color_gradient(low="orange",high="blue") +
  ggtitle("Domino")

# Mister
p2<-ggplot(ty_data2,aes(x=time,y=count,group=year,color=year)) + 
  geom_line(aes(color=year)) +
  geom_point() +
  scale_color_gradient(low="orange",high="blue") +
  ggtitle("Mister")

grid.arrange(p1, p2, nrow=2)
```

## x:time, y:duration, gb:year
```{r error=FALSE,message=FALSE,warning=FALSE}
## Make a graph
# Domino
p1 <- ggplot(ty_data, aes(x=time, y=duration, group=year, color=year)) + 
  geom_line(aes(color=year)) + 
  geom_point() +
  scale_color_gradient(low="orange", high="blue") +
  ggtitle("Domino")

# Mister
p2<-ggplot(ty_data2, aes(x=time, y=duration, group=year, color=year)) + 
  geom_line(aes(color=year)) + 
  geom_point() +
  scale_color_gradient(low="orange", high="blue") +
  ggtitle("Mister")

grid.arrange(p1, p2, nrow=2)
```

## x:time, y:total, gb:year
```{r error=FALSE,message=FALSE,warning=FALSE}
## Make a graph
# Domino
p1 <- ggplot(ty_data, aes(x=time, y=total, group=year, color=year)) + 
  geom_line(aes(color=year)) + 
  geom_point() +
  scale_color_gradient(low="orange", high="blue") +
  ggtitle("Domino")

# Mister
p2<-ggplot(ty_data2, aes(x=time, y=total, group=year, color=year)) + 
  geom_line(aes(color=year)) + 
  geom_point() +
  scale_color_gradient(low="orange", high="blue") +
  ggtitle("Mister")

grid.arrange(p1, p2, nrow=2)
```

# (3) YEAR
## DATA PREPROCESSING
```{r error=FALSE,message=FALSE,warning=FALSE}
# Domino
d_data = data %>%
  group_by(year) %>%
  summarize (count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

# Mister
d_data2 = data2 %>%
  group_by(year) %>%
  summarize (count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))
```

## x:year, y:count (bar graph)
```{r error=FALSE,message=FALSE,warning=FALSE}
## Make a graph
# Domino
p1<-ggplot(d_data,aes(x=year,y=count)) + geom_col() + ggtitle("Domino")

# Mister
p2<-ggplot(d_data2,aes(x=year,y=count)) + geom_col() + ggtitle("Mister")

grid.arrange(p1,p2,ncol=2)
```

## x:year, y:duration (bar graph)
```{r error=FALSE,message=FALSE,warning=FALSE}
## Make a graph
# Domino
p1<-ggplot(d_data,aes(x=year,y=duration)) + geom_col() + ggtitle("Domino")

# Mister
p2<-ggplot(d_data2,aes(x=year,y=duration)) + geom_col() + ggtitle("Mister")

grid.arrange(p1,p2,ncol=2)
```

## x:year, y:total (bar graph)
```{r error=FALSE,message=FALSE,warning=FALSE}
## Make a graph
# Domino
p1<-ggplot(d_data,aes(x=year,y=total)) + geom_col() + ggtitle("Domino")

# Mister
p2<-ggplot(d_data2,aes(x=year,y=total)) + geom_col() + ggtitle("Mister")

grid.arrange(p1,p2,ncol=2)
```

# (4) MONTH
## DATA PREPROCESSING
```{r error=FALSE,message=FALSE,warning=FALSE}
# Domino
my_data = data %>%
  group_by(month,year) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

# Mister
my_data2 = data2 %>%
  group_by(month,year) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))
```

## x:month, y:count, gb:year
```{r error=FALSE,message=FALSE,warning=FALSE}
## Make a graph
# Domino
p1<-ggplot(my_data,aes(x=as.factor(month),y=count,group=year,color=year)) + 
  geom_line(aes(color=year)) + 
  geom_point() +labs(x="month")+
  scale_color_gradient(low="orange",high="blue") +
  ggtitle("Domino")

# Mister
p2<-ggplot(my_data2,aes(x=as.factor(month),y=count,group=year,color=year)) + 
  geom_line(aes(color=year)) + labs(x="month")+
  geom_point() + 
  scale_color_gradient(low="orange",high="blue") + 
  ggtitle("Mister")

grid.arrange(p1,p2,nrow=2)
```

## x:month, y:duration, gb:year
```{r error=FALSE,message=FALSE,warning=FALSE}
## Make a graph
# Domino
p1<-ggplot(my_data,aes(x=as.factor(month),y=duration,group=year,color=year)) + 
  geom_line(aes(color=year)) + labs(x="month")+
  geom_point() +
  scale_color_gradient(low="orange",high="blue") +
  ggtitle("Domino")

# Mister
p2<-ggplot(my_data2,aes(x=as.factor(month),y=duration,group=year,color=year)) + 
  geom_line(aes(color=year)) + labs(x="month")+
  geom_point() + 
  scale_color_gradient(low="orange",high="blue") + 
  ggtitle("Mister")

grid.arrange(p1,p2,nrow=2)
```

## x:month, y:total, gb:year
```{r error=FALSE,message=FALSE,warning=FALSE}
## Make a graph
# Domino
p1<-ggplot(my_data,aes(x=as.factor(month), y=total, group=year, color=year)) + 
  geom_line(aes(color=year)) +labs(x="month")+ 
  geom_point() +
  scale_color_gradient(low="orange",high="blue") +
  ggtitle("Domino")

# Mister
p2<-ggplot(my_data2,aes(x=as.factor(month), y=total, group=year, color=year)) + 
  geom_line(aes(color=year)) + labs(x="month")+
  geom_point() + 
  scale_color_gradient(low="orange",high="blue") + 
  ggtitle("Mister")

grid.arrange(p1, p2, nrow=2)
```

# (5) WDAY
## x:wday, y:count 
* Sunday > Saturday > Friday
```{r error=FALSE,message=FALSE,warning=FALSE}
## Data preprocessing
# Domino
w_data = data %>%
  group_by(wday) %>%
  summarize (count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

# Mister
w_data2 = data2 %>%
  group_by(wday) %>%
  summarize (count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

## Make a graph
labels <- c("Mon", "Tues", "Wed", "Thurs", "Fri", "Sat", "Sun")

# Domino
p1<-ggplot(w_data,aes(x=factor(wday,levels=labels,ordered=TRUE),y=count)) + ylim(0,900)+
  geom_col()+labs(x="wday")+
  ggtitle("Domino")

# Mister
p2<-ggplot(w_data2,aes(x=factor(wday,levels=labels,ordered=TRUE),y=count)) + ylim(0,900)+ 
  geom_col()+labs(x="wday")+
  ggtitle("Mister")

grid.arrange(p1,p2,nrow=2)

# Compare domino and mister
p3<-ggplot(w_data,aes(x=factor(wday,levels=labels,ordered=TRUE),y=count,group=1)) + geom_line(colour="red")+labs(x="wday")
p3<-p3+ geom_line(data=w_data2,aes(x=factor(wday,levels=labels,ordered=TRUE),y=count,group=1),colour="blue") 
print(p3)
```

## x:wday, y:count, gb:year
* Sunday > Saturday > Friday
```{r error=FALSE,message=FALSE,warning=FALSE}
## Data preprocessing
# Domino
wy_data = data %>%
  group_by(wday,year) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

# Mister
wy_data2 = data2 %>%
  group_by(wday,year) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

## Make a graph
labels <- c("Mon", "Tues", "Wed", "Thurs", "Fri", "Sat", "Sun")

# Domino
p1<-ggplot(wy_data,aes(x=factor(wday, levels=labels ,ordered=TRUE),y=count,group=year,color=year)) + 
  geom_line(aes(color=year)) + 
  geom_point() +labs(x="wday")+
  scale_color_gradient(low="orange",high="blue") + ylim(0,1300)+
  ggtitle("Domino")

# Mister
p2<-ggplot(wy_data2,aes(x=factor(wday, levels=labels ,ordered=TRUE),y=count,group=year,color=year)) + 
  geom_line(aes(color=year)) + 
  geom_point() +labs(x="wday")+
  scale_color_gradient(low="orange",high="blue") + ylim(0,1300)+
  ggtitle("Mister")

grid.arrange(p1,p2,nrow=2)
```

# (6) HOLIDAY
## x:holiday, y:count
* highest on one day holiday
```{r error=FALSE,message=FALSE,warning=FALSE}
## Data preprocessing
# Domino
h_data = data %>%
  group_by(holiday) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

# Mister
h_data2 = data2 %>%
  group_by(holiday) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

## Make a graph
# Domino
p1<-ggplot(h_data, aes(x=holiday,y=count))+geom_col()+ ylim(0,1000)+ ggtitle("Domino")

# Mister
p2<-ggplot(h_data2, aes(x=holiday,y=count))+geom_col()+ylim(0,1000)+ ggtitle("Mister")

grid.arrange(p1,p2,ncol=2)
```

## holiday 3 days+
```{r error=FALSE,message=FALSE,warning=FALSE}
## Data preprocessing
# Domino
h_data = filter(data, holiday2!=0)
h <- h_data %>%
  group_by(holiday2) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

# Mister
h_data2 = filter(data2, holiday2!=0)
h2 <- h_data2 %>%
  group_by(holiday2) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

## Make a graph
# Domino
p1<-ggplot(h, aes(x=holiday2, y=count))+ 
  ylim(0,800)+
  geom_col()+
  ggtitle("Domino")

# Mister
p2<-ggplot(h2, aes(x=holiday2, y=count))+
  ylim(0,800)+
  geom_col()+
  ggtitle("Mister")

grid.arrange(p1,p2,ncol=2)
```

# (7) HOLIDAY vs WEEKEND
## x:holiday, y:count
* highest on one day holiday
```{r error=FALSE,message=FALSE,warning=FALSE}
## Data preprocessing
# 0:weekday 1:weekend
data$weekend <- ifelse(data$wday=="Sat", 1, ifelse(data$wday=="Sun", 1, 0))
data$weekend <- as.factor(data$weekend)

data2$weekend <- ifelse(data2$wday=="Sat", 1, ifelse(data2$wday=="Sun", 1, 0))
data2$weekend <- as.factor(data2$weekend)

# Domino
h_data = subset(data, (holiday==1 | holiday==2 | holiday==3))

domino <- h_data %>%
  group_by(weekend, holiday) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE))

# Mister
h_data2 = subset(data2, (holiday==1 | holiday==2 | holiday==3))

mister <- h_data2 %>%
  group_by(weekend, holiday) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE))

## Make a graph
# Domino
bar <- ggplot(domino, aes(x=holiday, y=count, fill=weekend))
p1<- bar + geom_bar(stat="identity", position="dodge")+ ylim(0,1000) + ggtitle("Domino")

# Mister
bar <- ggplot(mister, aes(x=holiday, y=count, fill=weekend))
p2<- bar + geom_bar(stat="identity", position="dodge")+ ylim(0,1000) + ggtitle("Mister")

grid.arrange(p1,p2,ncol=2)
```

# (8) weekend vs weekday
*0:weekday 1:weekend
```{r error=FALSE,message=FALSE,warning=FALSE}
## Data preprocessing
# Domino
data$weekend <- ifelse(data$wday=="Sat", 1, ifelse(data$wday=="Sun", 1, 0))
data$weekend <- as.factor(data$weekend)
w_data <- data %>%
  group_by(weekend) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE))

# Mister
data2$weekend<-ifelse(data2$wday=="Sat", 1, ifelse(data2$wday=="Sun", 1, 0))
data2$weekend <- as.factor(data2$weekend)
w_data2 <- data2 %>%
  group_by(weekend) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE))

## Make a graph
# Domino
p1<-ggplot(w_data, aes(x=weekend,y=count))+geom_col()+ggtitle("Domino")+labs(y="count") + ylim(0,800)

# Mister
p2<-ggplot(w_data2, aes(x=weekend,y=count))+geom_col()+ggtitle("Mister")+labs(y="count") + ylim(0,800)

grid.arrange(p1,p2,ncol=2)
```

# (9) PRECIPITATION
## DATA PREPROCESSING
```{r error=FALSE,message=FALSE,warning=FALSE}
# Domino
precClass_data = data %>%
  group_by(precClass) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

# Mister
precClass_data2 = data2 %>%
  group_by(precClass) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))
```

## x:precClass, y:count
* highest in rainy days
* lowest in clear days
```{r error=FALSE,message=FALSE,warning=FALSE}
## Make a graph
# Domino
p1<-ggplot(precClass_data,aes(x=precClass,y=count),na.rm=TRUE) + 
  geom_col() + ylim(0,1000)+
  ggtitle("Domino")

# Mister
p2<-ggplot(precClass_data2,aes(x=precClass,y=count),na.rm=TRUE) + ylim(0,1000)+
  geom_col() + 
  ggtitle("Mister")

grid.arrange(p1,p2,ncol=2)
```

## x:precClass, y:duration
```{r error=FALSE,message=FALSE,warning=FALSE}
## Make a graph
# Domino
p1<-ggplot(precClass_data,aes(x=precClass,y=duration),na.rm=TRUE) + ylim(0,125)+
  geom_col() + 
  ggtitle("Domino")

# Mister
p2<-ggplot(precClass_data2,aes(x=precClass,y=duration),na.rm=TRUE) + ylim(0,125)+
  geom_col() + 
  ggtitle("Mister")

grid.arrange(p1,p2,ncol=2)
```

## x:precClass, y:total
```{r error=FALSE,message=FALSE,warning=FALSE}
## Make a graph
# Domino
p1<-ggplot(precClass_data,aes(x=precClass,y=total),na.rm=TRUE) + ylim(0,120000)+
  geom_col() + 
  ggtitle("Domino")

# Mister
p2<-ggplot(precClass_data2,aes(x=precClass,y=total),na.rm=TRUE) + ylim(0,120000)+
  geom_col() + 
  ggtitle("Mister")

grid.arrange(p1,p2,ncol=2)
```


# (10) TEMPERATURE
## DATA PREPROCESSING
```{r error=FALSE,message=FALSE,warning=FALSE}
# Domino
tempClass_data = data %>%
  group_by(tempClass) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

# Mister
tempClass_data2 = data2 %>%
  group_by(tempClass) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))
```

## x:tempClass, y:count
* highest in cold days
* lowest in warm days
```{r error=FALSE,message=FALSE,warning=FALSE}
p1<- ggplot(tempClass_data,aes(x=tempClass,y=count),na.rm=TRUE)+  ylim(0,700)+
  geom_col()+
  ggtitle("Domino")

p2<- ggplot(tempClass_data2,aes(x=tempClass,y=count),na.rm=TRUE)+ ylim(0,700)+
  geom_col()+
  ggtitle("Mister")

grid.arrange(p1,p2,ncol=2)
```

## x:tempClass, y:duration
```{r error=FALSE,message=FALSE,warning=FALSE}
# Domino
p1<- ggplot(tempClass_data,aes(x=tempClass,y=duration),na.rm=TRUE)+  ylim(0,125)+
  geom_col()+
  ggtitle("Domino")

# Mister
p2<- ggplot(tempClass_data2,aes(x=tempClass,y=duration),na.rm=TRUE)+  ylim(0,125)+
  geom_col()+
  ggtitle("Mister")

grid.arrange(p1,p2,ncol=2)
```

## x:tempClass, y:total
```{r error=FALSE,message=FALSE,warning=FALSE}
# Domino
p1<- ggplot(tempClass_data,aes(x=tempClass,y=total),na.rm=TRUE)+  ylim(0,75000)+
  geom_col()+
  ggtitle("Domino")

# Mister
p2<- ggplot(tempClass_data2,aes(x=tempClass,y=total),na.rm=TRUE)+ylim(0,75000)+
  geom_col()+
  ggtitle("Mister")

grid.arrange(p1,p2,ncol=2)
```

# (12) SPORTS - Sochi 2014 Winter Olympics
## x:time, y:count, gb:sports
* sports - 0:default, 1:minor, 2:major
```{r error=FALSE,message=FALSE,warning=FALSE}
# Data preprocessing
# Domino
data$sports <- as.factor(data$sports)
so_data_2014 <- subset(data, year==2014)

sot_data <- so_data_2014 %>%
  group_by(sports, time) %>%
  summarize (count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

sot_data$time = as.factor(sot_data$time)

# Mister
data2$sports <- as.factor(data2$sports)
so_data2_2014 <- subset(data2, year==2014)

sot_data2 <- so_data2_2014 %>%
  group_by(sports, time) %>%
  summarize (count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

sot_data2$time = as.factor(sot_data2$time)

## Make a graph
# Domino
p1<-ggplot(sot_data, aes(x=time, y=count, group=sports, color=sports, linetype=sports)) + ylim(0,1200)+
  geom_line(lwd=2) +
  ylim(0, max(sot_data$count)) +
  ggtitle("Domino")

# Mister
p2<-ggplot(sot_data2, aes(x=time, y=count, group=sports, color=sports, linetype=sports)) + ylim(0,1200)+
  geom_line(lwd=2) +
  ylim(0, max(sot_data2$count)) +
  ggtitle("Mister")

grid.arrange(p1,p2,nrow=2)

```


## x:time, y:duration
```{r error=FALSE,message=FALSE,warning=FALSE}
# Domino
data$sports <- as.factor(data$sports)
so_data_2014 <- subset(data, year==2014)

sot_data <- so_data_2014 %>%
  group_by(sports, time) %>%
  summarize (count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

sot_data$time = as.factor(sot_data$time)

# Mister
data2$sports <- as.factor(data2$sports)
so_data2_2014 <- subset(data2, year==2014)

sot_data2 <- so_data2_2014 %>%
  group_by(sports, time) %>%
  summarize (count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

sot_data2$time = as.factor(sot_data2$time)

## Make a graph
# Domino
p1<-ggplot(sot_data, aes(x=time, y=duration, group=sports, color=sports, linetype=sports)) + ylim(70,130)+
  geom_line(lwd=2) +
  ggtitle("Domino")

# Mister
p2<-ggplot(sot_data2, aes(x=time, y=duration, group=sports, color=sports, linetype=sports)) + ylim(70,130)+
  geom_line(lwd=2) +
  ggtitle("Mister")

grid.arrange(p1,p2,nrow=2)
```