---
title: 'Call Center Data Analysis'
author: "jinyoung, hyunah, suyoung, yunhwan"
date: '20170807'
output:
  word_document: default
  html_document: default
---

## Call data import
```{r error=FALSE,message=FALSE,warning=FALSE}
data<-read.csv("domino6_2.csv", header=TRUE)
data2<-read.csv("mister2_2.csv", header=TRUE)
```

##Install Library
```{r error=FALSE,message=FALSE,warning=FALSE}
library(rpart.plot)
library(gplots)
library(xts)
library(dplyr)
library(tidyr)
library(ggplot2)
library(sqldf)
require('gridExtra')
```  

##(1) x:daily(7days), y:count
```{r error=FALSE,message=FALSE,warning=FALSE}
#domino
count=as.numeric(as.factor(data$count))
c_data <- as.xts(count,order.by=as.Date(data$date))
c_weekly <- apply.weekly(c_data,mean)

#mister
count2=as.numeric(as.factor(data2$count))
c_data2 <- as.xts(count2,order.by=as.Date(data2$date))
c2_weekly <- apply.weekly(c_data2,mean)

#view graph
par(mfrow=c(1,2))
plot(c_weekly, main="Domino", xlab="daily(7days)", ylab="count", xlim=c(0,1000))
plot(c2_weekly, main="Mister",xlab="daily(7days)", ylab="count", xlim=c(0,1000))
```

## (2)x:time, y:count, gb:year
* highest number of calls for dinnertime
* lowest for opening/closing time
```{r error=FALSE,message=FALSE,warning=FALSE}
# domino
ty_data = data %>%
  group_by(time,year) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

# mister
ty_data2 = data2 %>%
  group_by(time,year) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

#view graph
p1<-ggplot(ty_data,aes(x=time,y=count,group=year,color=year))+
  geom_line(aes(color=year))+
    geom_point() +
  scale_color_gradient(low="orange",high="blue") +
  ggtitle("Domino")

p2<-ggplot(ty_data2,aes(x=time,y=count,group=year,color=year))+
  geom_line(aes(color=year))+
    geom_point() +
  scale_color_gradient(low="orange",high="blue") +
  ggtitle("Mister")

grid.arrange(p1,p2,ncol=2)

```


##(3) x: year, y:count (bar graph)
```{r error=FALSE,message=FALSE,warning=FALSE}
#domino
d_data = data %>%
  group_by(year) %>%
  summarize (count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE),
            dust=mean(as.numeric(as.character(dust)),na.rm=TRUE))

#mister
d_data2 = data2 %>%
  group_by(year) %>%
  summarize (count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE),
            dust=mean(as.numeric(as.character(dust)),na.rm=TRUE))


#view graph
p1<-ggplot(d_data,aes(x=year,y=count)) + geom_col() + ggtitle("Domino")
p2<-ggplot(d_data2,aes(x=year,y=count)) + geom_col() + ggtitle("Mister")
grid.arrange(p1,p2,ncol=2)

```

##(4) x:month, y:count, gb:year
```{r error=FALSE,message=FALSE,warning=FALSE}
#domino
my_data = data %>%
  group_by(month,year) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

#mister
my_data2 = data2 %>%
  group_by(month,year) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

#view graph
p1<-ggplot(my_data,aes(x=month,y=count,group=year,color=year))+
  geom_line(aes(color=year))+
  geom_point() +
  scale_color_gradient(low="orange",high="blue") +
  ggtitle("Domino")

p2<-ggplot(my_data2,aes(x=month,y=count,group=year,color=year))+
  geom_line(aes(color=year))+
  geom_point() +
  scale_color_gradient(low="orange",high="blue")+
  ggtitle("Mister")

grid.arrange(p1,p2,ncol=2)
```

##(5)-1 x:wday, y:count 
* Sunday > Saturday > Friday
```{r error=FALSE,message=FALSE,warning=FALSE}
# domino
w_data = data %>%
  group_by(wday) %>%
  summarize (count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))
labels <- c("Mon", "Tues", "Wed", "Thurs", "Fri", "Sat", "Sun")

# mister
w_data2 = data2 %>%
  group_by(wday) %>%
  summarize (count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))
labels <- c("Mon", "Tues", "Wed", "Thurs", "Fri", "Sat", "Sun")


#view graph
p1<-ggplot(w_data,aes(x=factor(wday,levels=labels,ordered=TRUE),y=count)) + 
  geom_col()+
  ggtitle("Domino")

p2<-ggplot(w_data2,aes(x=factor(wday,levels=labels,ordered=TRUE),y=count)) + 
  geom_col()+
  ggtitle("Mister")

grid.arrange(p1,p2,ncol=2)
```



##(5)-2x:wday, y:count, gb:year
* Sunday > Saturday > Friday
```{r error=FALSE,message=FALSE,warning=FALSE}
#domino
wy_data = data %>%
  group_by(wday,year) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))
labels <- c("Mon", "Tues", "Wed", "Thurs", "Fri", "Sat", "Sun")

#mister
wy_data2 = data2 %>%
  group_by(wday,year) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))
labels <- c("Mon", "Tues", "Wed", "Thurs", "Fri", "Sat", "Sun")

#view graph
p1<-ggplot(wy_data,aes(x=factor(wday, levels=labels ,ordered=TRUE),y=count,group=year,color=year))+
  geom_line(aes(color=year))+
    geom_point() +
  scale_color_gradient(low="orange",high="blue") +
  ggtitle("Domino")

p2<-ggplot(wy_data2,aes(x=factor(wday, levels=labels ,ordered=TRUE),y=count,group=year,color=year))+
  geom_line(aes(color=year))+
    geom_point() +
  scale_color_gradient(low="orange",high="blue") +
  ggtitle("Mister")

grid.arrange(p1,p2,ncol=2)
```

## (6)-1 x:holiday, y:count
* highest on one day holiday
```{r error=FALSE,message=FALSE,warning=FALSE}
# domino
h_data = data %>%
  group_by(holiday) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

# mister
h_data2 = data2 %>%
  group_by(holiday) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

#view graph
p1<-ggplot(h_data, aes(x=holiday,y=count))+geom_col()+ggtitle("Domino")
p2<-ggplot(h_data2, aes(x=holiday,y=count))+geom_col()+ggtitle("Mister")

grid.arrange(p1,p2,ncol=2)
```


#(6)-2 holiday 3 days+
```{r error=FALSE,message=FALSE,warning=FALSE}

#domino
h_data = data 
k_data = filter(h_data,holiday2!=0)
d_data<-group_by(k_data, holiday2) 
v_data1<-summarize(d_data, count1=mean(as.numeric(as.character(count)),na.rm=TRUE),duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),total=mean(as.numeric(as.character(total)),na.rm=TRUE))

#mister
h_data2 = data2
k_data2 = filter(h_data2,holiday2!=0)
d_data2<-group_by(k_data2, holiday2) 
v_data2<-summarize(d_data2, count2=mean(as.numeric(as.character(count)),na.rm=TRUE),duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),total=mean(as.numeric(as.character(total)),na.rm=TRUE))

#view graph
ggplot(v_data1, aes(x=holiday2,y=count1))+
  geom_col()+
  ggtitle("Domino")
ggplot(v_data2, aes(x=holiday2,y=count2))+
  geom_col()+
  ggtitle("Mister")

grid.arrange(p1,p2,ncol=2)
```

#(8) weekend vs week
*0:weekday 1:weekend
```{r error=FALSE,message=FALSE,warning=FALSE}

#domino
h_data1 = data 
h_data1$weekend<-ifelse(h_data1$wday=="Sat", 1,ifelse(h_data1$wday=="Sun", 1, 0) )
d_data1<-group_by(h_data1, weekend)
v_data1<-summarize(d_data1, count1=mean(as.numeric(as.character(count)),na.rm=TRUE))

#mister
h_data2 = data2 
h_data2$weekend<-ifelse(h_data2$wday=="Sat", 1,ifelse(h_data2$wday=="Sun", 1, 0) )
d_data2<-group_by(h_data2, weekend)
v_data2<-summarize(d_data2, count2=mean(as.numeric(as.character(count)),na.rm=TRUE))

#view graph
p1<-ggplot(v_data1, aes(x=weekend,y=count1))+geom_col()+ggtitle("Domino")
p2<-ggplot(v_data2, aes(x=weekend,y=count2))+geom_col()+ggtitle("Mister")

grid.arrange(p1,p2,ncol=2)
```


## (9) x:precClass, y:count
* highest in rainy days
* lowest in clear days
* H:precipitation 5mm ?´?ƒ, L:0~5mm, N:0mm
```{r error=FALSE,message=FALSE,warning=FALSE}
# domino
precClass_data = data %>%
  group_by(precClass) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

# mister
precClass_data2 = data2 %>%
  group_by(precClass) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

#view graph
p1<-ggplot(precClass_data,aes(x=precClass,y=count),na.rm=TRUE)+
  geom_col()+
  ggtitle("Domino")

#graph
p2<-ggplot(precClass_data2,aes(x=precClass,y=count),na.rm=TRUE)+
  geom_col()+
  ggtitle("Mister")

grid.arrange(p1,p2,ncol=2)

```

##(10) x:tempClass, y:count
* highest in cold days
* lowest in warm days
```{r error=FALSE,message=FALSE,warning=FALSE}
# domino
tempClass_data = data %>%
  group_by(tempClass) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

# mister
tempClass_data2 = data2 %>%
  group_by(tempClass) %>%
  summarize(count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

#view graph
p1<- ggplot(tempClass_data,aes(x=tempClass,y=count),na.rm=TRUE)+
  geom_col()+
  ggtitle("Domino")

#graph
p2<- ggplot(tempClass_data2,aes(x=tempClass,y=count),na.rm=TRUE)+
  geom_col()+
  ggtitle("Mister")

grid.arrange(p1,p2,ncol=2)

```


# SPORTS - Sochi 2014 Winter Olympics
##(12)-1 x:time, y:count, gb:sports
* sports - 0:default, 1:minor, 2:major
```{r error=FALSE,message=FALSE,warning=FALSE}
# domino
data$sports <- as.factor(data$sports)
so_data_2014 <- subset(data, year==2014)

sot_data <- so_data_2014 %>%
  group_by(sports, time) %>%
  summarize (count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

sot_data$time = as.factor(sot_data$time)

# mister
data2$sports <- as.factor(data2$sports)
so_data2_2014 <- subset(data2, year==2014)

sot_data2 <- so_data2_2014 %>%
  group_by(sports, time) %>%
  summarize (count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

sot_data2$time = as.factor(sot_data2$time)

#view graph
p1<-ggplot(sot_data, aes(x=time, y=count, group=sports, color=sports, linetype=sports)) + 
  geom_line(lwd=2) +
  ylim(0, max(sot_data$count)) +
  ggtitle("Domino")

p2<-ggplot(sot_data2, aes(x=time, y=count, group=sports, color=sports, linetype=sports)) + 
  geom_line(lwd=2) +
  ylim(0, max(sot_data2$count)) +
  ggtitle("Mister")

grid.arrange(p1,p2,ncol=2)

```


## (12)-2x:time, y:duration
```{r error=FALSE,message=FALSE,warning=FALSE}
# Domino
data$sports <- as.factor(data$sports)
so_data_2014 <- subset(data, year==2014)

sot_data <- so_data_2014 %>%
  group_by(sports, time) %>%
  summarize (count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

sot_data$time = as.factor(sot_data$time)

# Mister
data2$sports <- as.factor(data2$sports)
so_data2_2014 <- subset(data2, year==2014)

sot_data2 <- so_data2_2014 %>%
  group_by(sports, time) %>%
  summarize (count=mean(as.numeric(as.character(count)),na.rm=TRUE),
            duration=mean(as.numeric(as.character(duration)),na.rm=TRUE),
            total=mean(as.numeric(as.character(total)),na.rm=TRUE))

sot_data2$time = as.factor(sot_data2$time)

#view graph
p1<-ggplot(sot_data, aes(x=time, y=duration, group=sports, color=sports, linetype=sports)) + 
  geom_line(lwd=2) +
  ggtitle("Domino")

p2<-ggplot(sot_data2, aes(x=time, y=duration, group=sports, color=sports, linetype=sports)) + 
  geom_line(lwd=2) +
  ggtitle("Mister")

grid.arrange(p1,p2,ncol=2)
```