---
title: "Call Center Data Analysis"
author: "jinyoung, hyunah, suyoung, yunhwan"
date: '20170809'
output:
  word_document: default
  html_document: default
--- 

## Call data import
```{r error=FALSE,message=FALSE,warning=FALSE}
getwd()
setwd("/Users/suyoung/Desktop")
data<-read.csv("mister.csv", header=TRUE)

```

## Install Library
```{r error=FALSE,message=FALSE,warning=FALSE}
install.packages("e1071")
install.packages("rpart.plot")
library(e1071)
library(randomForest)
library(caret)
library(dplyr)
library(rpart.plot)
library(ggplot2)

```

# totalClass와 RF 선택 이유
## DECISION TREE (RPART)
## PREPROCESSING
```{r error=FALSE,message=FALSE,warning=FALSE}
myData <- subset(data, select = c(year, month, time, wday, holiday, precClass, tempClass,total))
myData$year <- as.factor(myData$year)
myData$month <- as.factor(myData$month)
myData$time <- as.factor(myData$time)
myData$holiday <- as.factor(myData$holiday)
myData$precClass <- as.factor(myData$precClass)
myData$tempClass <- as.factor(myData$tempClass)
myData$wday <- as.factor(myData$wday)

# Remove NA
myData <- myData[complete.cases(myData),]
```

## DECISION TREE (RPART)
## totalClass3
```{r error=FALSE,message=FALSE,warning=FALSE}
# create totalClass3
myData$totalClass3 <- ntile(myData$total, 3)
myData$totalClass3 <- as.factor(myData$totalClass3)

# Partition data set into training and test
sample_idx3 <- createDataPartition(y=myData$totalClass3, p=0.7, list=FALSE)
trainData3 <- myData[sample_idx3, ]
testData3 <- myData[-sample_idx3, ]

# Build a Decision Tree model
model3 <- rpart(totalClass3 ~year+time+month+holiday+precClass+tempClass+wday, data=trainData3, control=rpart.control(cp=0, maxdepth=4), method='class')

# Build pruned tree
pruned_model3 <- prune(model3, cp=model3$cptable[which.min(model3$cptable[,"xerror"]), "CP"])

# Compute accuracy of pruned model
prediction3 <- predict(pruned_model3, testData3, type='class')
confusionMatrix(prediction3, testData3$totalClass3)
```

## DECISION TREE (RPART)
## totalClass4
```{r error=FALSE,message=FALSE,warning=FALSE}
# create totalClass3
myData$totalClass4 <- ntile(myData$total, 4)
myData$totalClass4 <- as.factor(myData$totalClass4)

summary(myData$totalClass4)
# Partition data set into training and test
sample_idx4 <- createDataPartition(y=myData$totalClass4, p=0.7, list=FALSE)
trainData4 <- myData[sample_idx4, ]
testData4 <- myData[-sample_idx4, ]

# Build a Decision Tree model
model4 <- rpart(totalClass4 ~year+time+month+holiday+precClass+tempClass+wday, data=trainData4, control=rpart.control(cp=0, maxdepth=4), method='class')

# Build pruned tree
pruned_model4 <- prune(model4, cp=model4$cptable[which.min(model4$cptable[,"xerror"]), "CP"])

# Compute accuracy of pruned model
prediction4 <- predict(pruned_model4, testData4, type='class')
confusionMatrix(prediction4, testData4$totalClass4)
```

## DECISION TREE (RPART)
## totalClass8
```{r error=FALSE,message=FALSE,warning=FALSE}
# create totalClass3
myData$totalClass8 <- ntile(myData$total, 8)
myData$totalClass8 <- as.factor(myData$totalClass8)

# Partition data set into training and test
sample_idx8 <- createDataPartition(y=myData$totalClass8, p=0.7, list=FALSE)
trainData8 <- myData[sample_idx8, ]
testData8 <- myData[-sample_idx8, ]

# Build a Decision Tree model
model8 <- rpart(totalClass8 ~year+time+month+holiday+precClass+tempClass+wday, data=trainData8, control=rpart.control(cp=0, maxdepth=4), method='class')

# Build pruned tree
pruned_model8 <- prune(model8, cp=model8$cptable[which.min(model8$cptable[,"xerror"]), "CP"])

# Compute accuracy of pruned model
prediction8 <- predict(pruned_model8, testData8, type='class')
confusionMatrix(prediction8, testData8$totalClass8)
```

## RANDOM FOREST 
## Preprocessing
```{r error=FALSE,message=FALSE,warning=FALSE}
myData <- subset(data, select = c(year, month, time, wday, holiday, precClass, tempClass,total))
myData$year <- as.factor(myData$year)
myData$month <- as.factor(myData$month)
myData$time <- as.factor(myData$time)
myData$holiday <- as.factor(myData$holiday)
myData$precClass <- as.factor(myData$precClass)
myData$tempClass <- as.factor(myData$tempClass)

# Remove NA
myData <- myData[complete.cases(myData),]
```

## RANDOM FOREST 
## totalClass3
```{r error=FALSE,message=FALSE,warning=FALSE}
# create totalClass3
myData$totalClass3 <- ntile(myData$total, 3)
myData$totalClass3 <- as.factor(myData$totalClass3)

# Partition data set into training and test
sample_idx3 <- createDataPartition(y=myData$totalClass3, p=0.7, list=FALSE)
trainData3 <- myData[sample_idx3, ]
testData3 <- myData[-sample_idx3, ]

# Build a randomForest model
model3 <- randomForest(totalClass3~year+month+time+wday+holiday+precClass+tempClass, data=trainData3, importance=TRUE)

# Predict accuracy
prediction3 <- predict(model3, testData3, type='class')
confusionMatrix(prediction3, testData3$totalClass3)
```

## RANDOM FOREST 
## totalClass4
```{r error=FALSE,message=FALSE,warning=FALSE}
# create totalClass4
myData$totalClass4 <- ntile(myData$total, 4)
myData$totalClass4 <- as.factor(myData$totalClass4)

# Partition data set into training and test
sample_idx4 <- createDataPartition(y=myData$totalClass4, p=0.7, list=FALSE)
trainData4 <- myData[sample_idx4, ]
testData4 <- myData[-sample_idx4, ]

# Build a randomForest model
model4 <- randomForest(totalClass4~year+month+time+wday+holiday+precClass+tempClass, data=trainData4, importance=TRUE)

## Predict accuracy
prediction4 <- predict(model4, testData4, type='class')
confusionMatrix(prediction4, testData4$totalClass4)
```

## RANDOM FOREST 
## totalClass8
```{r error=FALSE,message=FALSE,warning=FALSE}
# create totalClass8
myData$totalClass8 <- ntile(myData$total, 8)
myData$totalClass8 <- as.factor(myData$totalClass8)

# Partition data set into training and test
sample_idx8 <- createDataPartition(y=myData$totalClass8, p=0.7, list=FALSE)
trainData8 <- myData[sample_idx8, ]
testData8 <- myData[-sample_idx8, ]

# Build a randomForest model
model8 <- randomForest(totalClass8~year+month+time+wday+holiday+precClass+tempClass, data=trainData8, importance=TRUE)

# Predict accuracy
prediction8 <- predict(model8, testData8, type='class')
confusionMatrix(prediction8, testData8$totalClass8)
```

## XGBOOST
## Preprocessing
```{r error=FALSE,message=FALSE,warning=FALSE}
# Preprocessing
myData <- subset(data, select = c(year, month, time, wday_num, holiday, prec,temp,total))
myData$year <- as.numeric(myData$year)
myData$month <- as.numeric(myData$month)
myData$time <- as.numeric(myData$time)
myData$holiday <- as.numeric(myData$holiday)
myData$prec <- as.numeric(myData$prec)
myData$temp <- as.numeric(myData$temp)
myData$wday_num <- as.numeric(myData$wday_num)

# Remove NA
myData <- myData[complete.cases(myData),]
```

## XGBOOST
## totalClass3
```{r error=FALSE,message=FALSE,warning=FALSE}
# Partition data set into training and test
sample_idx3 <- createDataPartition(y=myData$total, p=0.7, list=FALSE)
trainData3 <- myData[sample_idx3, ]
testData3 <- myData[-sample_idx3, ]

# Build a xgboost model 
features = c("year","temp","prec","month","time","wday_num","holiday")

model3 = xgboost(data=data.matrix(trainData3[,features]), label=trainData3$total,
            max_depth=3, eta=0.005, nround=3000, nthread=2, objective="reg:linear")

# Predict Accuracy
testData3$pred = predict(model3, data.matrix(testData3[,features]))

testData3$totalClass3 <- ntile(testData3$total, 3)
testData3$predClass3 <- ntile(testData3$pred,3)

prediction3<-testData3$predClass3
confusionMatrix(prediction3, testData3$totalClass3)
```

## XGBOOST
## totalClass4
```{r error=FALSE,message=FALSE,warning=FALSE}
# Partition data set into training and test
sample_idx4 <- createDataPartition(y=myData$total, p=0.7, list=FALSE)
trainData4 <- myData[sample_idx4, ]
testData4 <- myData[-sample_idx4, ]

# Build a xgboost model 
features = c("year","temp","prec","month","time","wday_num","holiday")

model4 = xgboost(data=data.matrix(trainData4[,features]), label=trainData4$total,
            max_depth=3, eta=0.005, nround=3000, nthread=2, objective="reg:linear")

# Predict Accuracy
testData4$pred = predict(model4, data.matrix(testData4[,features]))

testData4$totalClass4 <- ntile(testData4$total, 4)
testData4$predClass4 <- ntile(testData4$pred, 4)

prediction4<-testData4$predClass4
confusionMatrix(prediction4, testData4$totalClass4)
```

## XGBOOST
## totalClass8
```{r error=FALSE,message=FALSE,warning=FALSE}
# Partition data set into training and test
sample_idx8 <- createDataPartition(y=myData$totalClass8, p=0.7, list=FALSE)
trainData8 <- myData[sample_idx8, ]
testData8 <- myData[-sample_idx8, ]

# Build a xgboost model 
features = c("year","temp","prec","month","time","wday_num","holiday")

model8 = xgboost(data=data.matrix(trainData8[,features]), label=trainData8$total,
            max_depth=3, eta=0.005, nround=3000, nthread=2, objective="reg:linear")

# Predict Accuracy
testData8$pred = predict(model8, data.matrix(testData8[,features]))

testData8$totalClass8 <- ntile(testData8$total, 8)
testData8$predClass8 <- ntile(testData8$pred, 8)

prediction8<-testData8$predClass8
confusionMatrix(prediction8, testData8$totalClass8)
```

## SUPPORT VECTOR MACHINE
## Preprocessing
```{r error=FALSE,message=FALSE,warning=FALSE}
# Preprocessing
myData <- subset(data, select = c(year, month, time, wday, holiday, precClass,tempClass,total))

# Remove NA
myData <- myData[complete.cases(myData),]
```

## SUPPORT VECTOR MACHINE
## totalClass3
```{r error=FALSE,message=FALSE,warning=FALSE}
# Create totalClass3
myData$totalClass3 <- ntile(myData$total, 3)
myData$totalClass3 <- as.factor(myData$totalClass3)

# Partition data set into training and test
sample_idx3 <- createDataPartition(y=myData$totalClass3, p=0.7, list=FALSE)
trainData3 <- myData[sample_idx3, ]
testData3 <- myData[-sample_idx3, ]

# Build a SVM model
model3 = svm(totalClass3 ~ month+time+wday+holiday+precClass+tempClass+year, data = trainData3, type='C-classification')

# Predict Accuracy
prediction3<-predict(model3, newdata=testData3)
confusionMatrix(prediction3,testData3$totalClass3)
```

## SUPPORT VECTOR MACHINE
## totalClass4
```{r error=FALSE,message=FALSE,warning=FALSE}
# Create totalClass4
myData$totalClass4 <- ntile(myData$total, 4)
myData$totalClass4 <- as.factor(myData$totalClass4)

# Partition data set into training and test
sample_idx4 <- createDataPartition(y=myData$totalClass4, p=0.7, list=FALSE)
trainData4 <- myData[sample_idx4, ]
testData4 <- myData[-sample_idx4, ]

# Build a SVM model
model4 = svm(totalClass4 ~ month+time+wday+holiday+precClass+tempClass+year, data = trainData4, type='C-classification')

# Predict Accuracy
prediction4<-predict(model4, newdata=testData4)
confusionMatrix(prediction4,testData4$totalClass4)
```

## SUPPORT VECTOR MACHINE
## totalClass8
```{r error=FALSE,message=FALSE,warning=FALSE}
# Create totalClass4
myData$totalClass8 <- ntile(myData$total, 8)
myData$totalClass8 <- as.factor(myData$totalClass8)

# Partition data set into training and test
sample_idx8 <- createDataPartition(y=myData$totalClass8, p=0.7, list=FALSE)
trainData8 <- myData[sample_idx8, ]
testData8 <- myData[-sample_idx8, ]

# Build a SVM model
model8 = svm(totalClass8 ~ month+time+wday+holiday+precClass+tempClass+year, data = trainData8, type='C-classification')

# Predict Accuracy
prediction8<-predict(model8, newdata=testData8)
confusionMatrix(prediction8,testData8$totalClass8)
```


#부분 데이터 학습 모델 vs 전체 데이터 학습 모델
## PREPROCESSING
```{r error=FALSE,message=FALSE,warning=FALSE}
# Preprocessing
myData <- subset(data, select = c(year, month, time, wday, holiday, precClass, tempClass, total))
myData$year <- as.factor(myData$year)
myData$month <- as.factor(myData$month)
myData$time <- as.factor(myData$time)
myData$holiday <- as.factor(myData$holiday)
myData$precClass <- as.factor(myData$precClass)
myData$tempClass <- as.factor(myData$tempClass)
myData$wday <- as.factor(myData$wday)

# Remove NA
myData <- myData[complete.cases(myData),]
```

# WITHOUT 10 & 22
##부분 데이터 학습 모델
```{r error=FALSE,message=FALSE,warning=FALSE}
# Remove 10, 22
wo10Data <- subset(myData, time!=10)
wo10Data <- subset(wo10Data, time!=22)

# create totalClass4
wo10Data$totalClass4 <- ntile(wo10Data$total, 4)
wo10Data$totalClass4 <- as.factor(wo10Data$totalClass4)

# Partition data set into training and test
sample_idx <- createDataPartition(y=wo10Data$totalClass4, p=0.7, list=FALSE)
wotrainData <- wo10Data[sample_idx, ]
wotestData <- wo10Data[-sample_idx, ]

# Build a model
features <- c("year", "month", "time", "wday", "holiday", "precClass", "tempClass", "totalClass4")
model <- randomForest(totalClass4~., data=wotrainData[,features], importance=TRUE)

# Predict accuracy
prediction <- predict(model, wotestData[,features], type='class')
confusionMatrix(prediction, wotestData$totalClass4)
```

# WITHOUT 10 & 22: PARTITION
## 전체 데이터 학습 모델
```{r error=FALSE,message=FALSE,warning=FALSE}
# 전체 데이터 학습 모델
myData$totalClass4 <- ntile(myData$total, 4)
myData$totalClass4 <- as.factor(myData$totalClass4)
sample_idx4 <- createDataPartition(y=myData$totalClass4, p=0.7, list=FALSE)
trainData4 <- myData[sample_idx4, ]
testData4 <- myData[-sample_idx4, ]
model4 <- randomForest(totalClass4~year+month+time+wday+holiday+precClass+tempClass, data=trainData4, importance=TRUE)

# Predict Accuracy
prediction <- predict(model4, wotestData[,features], type='class')
confusionMatrix(prediction, wotestData$totalClass4)

```


# WEEKDAY VS WEEKEND
##부분 데이터 학습 모델
## DATA PARTITION
```{r error=FALSE,message=FALSE,warning=FALSE}
# Partition into weekend vs weekday
id_weekend = which(myData$wday=="Sun"|myData$wday=="Sat")

weekend<-myData[id_weekend,]
weekday<-myData[-id_weekend,]

# Create Classes
weekend$weekendClass<-ntile(weekend$total, 4)
weekday$weekdayClass<-ntile(weekday$total, 4)

weekend$weekendClass<-as.factor(weekend$weekendClass)
weekday$weekdayClass<-as.factor(weekday$weekdayClass)
```

# WEEKDAY VS WEEKEND
##부분 데이터 학습 모델
## WEEKDAY
```{r error=FALSE,message=FALSE,warning=FALSE}
# Partition data set into training and test
sample_idx <- sample(1:nrow(weekday), nrow(weekday)*0.7, replace = F)
weekdayTrain <- weekday[sample_idx, ]
weekdayTest <- weekday[-sample_idx, ]

# Build a model
model<-randomForest(weekdayTrain$weekdayClass~month+time+wday+holiday+precClass+tempClass+year, data=weekdayTrain, importance=TRUE)

# Predict accuracy
prediction <- predict(model, weekdayTest, type='class')
confusionMatrix(prediction, weekdayTest$weekdayClass)
```

# WEEKDAY VS WEEKEND
##부분 데이터 학습 모델
## WEEKEND
```{r error=FALSE,message=FALSE,warning=FALSE}
# Partition data set into training and test
sample_idx <- sample(1:nrow(weekend), nrow(weekend)*0.7, replace = F)
weekendTrain <- weekend[sample_idx, ]
weekendTest <- weekend[-sample_idx, ]

# Build a model
model<-randomForest(weekendTrain$weekendClass~month+time+wday+holiday+precClass+tempClass+year, data=weekendTrain, importance=TRUE)

# Predict accuracy
prediction <- predict(model, weekendTest, type='class')
confusionMatrix(prediction, weekendTest$weekendClass)
```

# WEEKEND VS WEEKDAY
##전체 데이터 학습 모델
```{r error=FALSE,message=FALSE,warning=FALSE}

# Predict Accuracy for Weekend
prediction <- predict(model4, weekendTest[,features], type='class')
confusionMatrix(prediction, weekendTest$totalClass4)

# Predict Accuracy for Weekday
prediction <- predict(model4, weekdayTest[,features], type='class')
confusionMatrix(prediction, weekdayTest$totalClass4)

```

# PEAK(12, 18, 19) & NON-PEAK
## DATA PARTITION
```{r error=FALSE,message=FALSE,warning=FALSE}
# Partition into weekend vs weekday
id_peak = which(myData$time==12|myData$time==18|myData$time==19)

peak<-myData[id_peak,]
nonpeak<-myData[-id_peak,]

# Create Classes
peak$peakClass<-ntile(peak$total, 4)
nonpeak$nonpeakClass<-ntile(nonpeak$total, 4)

peak$peakClass<-as.factor(peak$peakClass)
nonpeak$nonpeakClass<-as.factor(nonpeak$nonpeakClass)
```

# PEAK(12, 18, 19) & NON-PEAK
## PEAK
```{r error=FALSE,message=FALSE,warning=FALSE}
# Partition data set into training and test
sample_idx <- sample(1:nrow(peak), nrow(peak)*0.7, replace = F)
peakTrain <- peak[sample_idx, ]
peakTest <- peak[-sample_idx, ]

# Build a model
model<-randomForest(peakTrain$peakClass~month+time+wday+holiday+precClass+tempClass+year, data=peakTrain, importance=TRUE)

# Predict accuracy
prediction <- predict(model, peakTest, type='class')
confusionMatrix(prediction, peakTest$peakClass)
```

# PEAK(12, 18, 19) & NON-PEAK
## NON-PEAK
```{r error=FALSE,message=FALSE,warning=FALSE}
# Partition data set into training and test
sample_idx <- sample(1:nrow(nonpeak), nrow(nonpeak)*0.7, replace = F)
nonpeakTrain <- nonpeak[sample_idx, ]
nonpeakTest <- nonpeak[-sample_idx, ]

# Build a model
model<-randomForest(nonpeakTrain$nonpeakClass~month+time+wday+holiday+precClass+tempClass+year, data=nonpeakTrain, importance=TRUE)

# Predict accuracy
prediction <- predict(model, nonpeakTest, type='class')
confusionMatrix(prediction, nonpeakTest$nonpeakClass)
```

# PEAK VS NONPEAK
##전체 데이터 학습 모델
```{r error=FALSE,message=FALSE,warning=FALSE}

# Predict Accuracy for Peak
prediction <- predict(model4, peakTest[,features], type='class')
confusionMatrix(prediction, peakTest$totalClass4)

# Predict Accuracy for nonPeak
prediction <- predict(model4, nonpeakTest[,features], type='class')
confusionMatrix(prediction, nonpeakTest$totalClass4)

```

# ERROR CASE
## 전체데이터학습모델
## MAKE A RANDOM FOREST 
## totalClass4
```{r error=FALSE,message=FALSE,warning=FALSE}
# create totalClass4
myData$totalClass4 <- ntile(myData$total, 4)
myData$totalClass4 <- as.factor(myData$totalClass4)

# Partition data set into training and test
sample_idx4 <- createDataPartition(y=myData$totalClass4, p=0.7, list=FALSE)
trainData4 <- myData[sample_idx4, ]
testData4 <- myData[-sample_idx4, ]

# Build a randomForest model
model4 <- randomForest(totalClass4~year+month+time+wday+holiday+precClass+tempClass, data=trainData4, importance=TRUE)

```


## RANDOM FOREST & TOTALCLASS4
## MONTH
```{r error=FALSE,message=FALSE,warning=FALSE}
testData4$prediction4 <- predict(model4, testData4, type='class')

error_id = which(testData4$totalClass4 != testData4$prediction4)
count<-testData4[error_id,]$month

plot(count, main="Error Case for Each Month", xlab="Month",ylab="Count")
```

# ERROR CASE
## RANDOM FOREST & TOTALCLASS4
## TIME
```{r error=FALSE,message=FALSE,warning=FALSE}
testData4$prediction4 <- predict(model4, testData4, type='class')

error_id = which(testData4$totalClass4 != testData4$prediction4)
count<-testData4[error_id,]$time

plot(count, main="Error Case for Each Time", xlab="Time",ylab="Count")

```

# ERROR CASE
## RANDOM FOREST & TOTALCLASS4
## WDAY
```{r error=FALSE,message=FALSE,warning=FALSE}

testData4$prediction4 <- predict(model4, testData4, type='class')

error_id = which(testData4$totalClass4 != testData4$prediction4)
count<-testData4[error_id,]$wday

plot(count, main="Error Case for Each Day", xlab="Day of the Week",ylab="Count")

```



